%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Shopify Inc.} % Organization
    {Production Engineer, Cloud Platform} % Job title
    {Ottawa, ON} % Location
    {May. 2016 - August. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Containerized and ported the internal image resizing service over to Google Cloud using Kubernetes.}
        \item {Worked on building a production ready platform as a service for internal developers using Docker and Kubernetes.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Shopify Inc.} % Organization
    {Production Engineer, Developer Acceleration} % Job title
    {Ottawa, ON} % Location
    {September. 2015 - April. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an on demand staging environment for developers to boot up standalone Shopify instances in the cloud.}
        \item {Built tools for developers to get access to production fidelity data during development.}
        \item {Worked on the production pipeline reducing the deployment time to from 25 to 15 minutes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Shopify Inc.} % Organization
    {Mobile and Backend Software Developer} % Job title
    {Ottawa, ON} % Location
    {May. 2014 - April. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built functionality to add discounts on individual products on Shopify for iPhone.}
        \item {Integrated 3rd party payment gateways into Shopify Point of Sale application.}
        \item {Designed and developed improved tools for the support team to help Shopify retail customers.}
      \end{cvitems}
    } 
    
%---------------------------------------------------------
  \cventry
    {Canadian Broadcasting Corporation} % Organization
    {iOS Developer} % Job title
    {Toronto, ON} % Location
    {September. 2013 - December. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a fully native iOS implementation for CBC’s news client.}
        \item {Implemented an HTML parser in Objective C to dynamically layout news articles in the application.}
      \end{cvitems}
    }       

%---------------------------------------------------------

\end{cventries}
