%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cvprojectentry
    {\href{https://github.com/devctl/devctl}{devctl}\ \faPaperclip} % Affiliation/role
    {Present}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developing a command line tool using golang, to simplify setting up and managing development environments.}
        \item {Currently implementing the ability to run docker containers for any required dependencies.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvprojectentry
    %{\faGithubSquare Hack the North Organizer} % Affiliation/role
	{\href{https://hackthenorth.com}{Hack the North Organizer}\ \faPaperclip}    
	{Jan 2015 - Present}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Part of the organizing team for Canada's largest hackathon in Waterloo,ON.}
        \item {Worked on the 2015 iOS application and managed volunteers in 2016.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvprojectentry
    {\href{http://devpost.com/software/tendr}{Tendr}\ \faPaperclip} % Affiliation/role
    {McHacks}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Built an iOS app that helps users to find their next meal.}
        \item {Won \textbf{1st Place} and a \textbf{Thiel Fellowship Grant} at McHacks 2015.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cvprojectentry
    {Code for Kids} % Affiliation/role
    {May 2014 - Jan 2015}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Volunteered for an Ottawa based nonprofit which aims to teach kids how to code.}
        \item {Helped organize and run events in Ottawa and started a Waterloo chapter.}
      \end{cvitems}
    }
  
%---------------------------------------------------------
  \cvprojectentry
    {\href{http://teamdave.ca/}{FIRST Robotics}\ \faPaperclip} % Affiliation/role
    {Jan 2014 - May 2015}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {One of the mentors for a local FIRST robotics team, Team Dave 3683.}
        \item {Worked with other mentors to help highschool students design, build and program robots as per the cometition requirements.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
